---
title: "Titre"
author: "Sébastien Guyader"
date: "`r format(Sys.Date(), '%Y %B %d')`"
output:
  pdf_document:
    fig_height: 5
    fig_width: 5
    latex_engine: xelatex
  html_document:
    df_print: paged
mainfont: Calibri
fontsize: 12pt
---

```{r, echo=FALSE}
library(knitr)
opts_chunk$set(dev.args=list(pointsize=10))
```

## Iris data

The iris data set gives data on the dimensions of sepals and petals measured on 50 samples of three different species of iris (setosa, versicolor and virginica).

```{r}
library(partykit)
```

We will construct a model of iris species as a function of the other covariates.

```{r}
iris.ct <- ctree(Species ~ .,data = iris)
plot(iris.ct)
```

Get the node p-values.

```{r}
nodeapply(iris.ct, ids = nodeids(iris.ct),
  FUN = function(n) info_node(n)$p.value
  )
```

The structure of the tree is essentially the same. Only the representation of the nodes differs because, whereas ozone was a continuous numerical variable, iris species is a categorical variable. The nodes are thus represented as bar plots. Node 2 is predominantly setosa, node 5 is mostly versicolor and node 7 is almost all viriginica. Node 6 is half versicolor and half virginica and corresponds to a category with long, narrow petals. It is interesting to note that the model depends only on the dimensions of the petals and not on those of the sepals.

We can assess the quality of the model by constructing a confusion matrix. This shows that the model performs perfectly for setosa irises. For versicolor it also performs very well, only classifying one sample incorrectly as a virginica. For virginica it fails to correctly classify 5 samples. The model seems to perform well overall, however, this is based on the training data, so it is not really an objective assessment!

```{r}
table(iris$Species, predict(iris.ct), dnn = c("Actual species",
                                              "Predicted species"))
```

Finally, we can use the model to predict the species for new data (no need to specify sepal length and width as they ar not use by the model).

```{r}
new.iris <- data.frame(Sepal.Length=rep(0,5), Sepal.Width=rep(0,5),
Petal.Length=c(1,4,5,4,5), Petal.Width=c(1,2,1,1,2))
predict(iris.ct, newdata = new.iris)
predict(iris.ct, newdata = new.iris, type="node")
```

## Air Quality data

Load Air quality dataset:
```{r}
airq <- subset(airquality, !is.na(Ozone))
airct <- ctree(Ozone ~ ., data = airq)
print(airct)
```

Summarize the data (TODO : use dplyr::summarise)
```{r}
tapply(airq$Ozone, predict(airct, type = "node"), function(y)
  c("n" = length(y), "Avg." = mean(y),
  "Variance" = var(y), "SSE" = sum((y - mean(y))^2))
  )
```

Test the significance of changes:
```{r}
library("strucchange")

sctest(airct)

nodeapply(airct, ids = nodeids(airct), FUN = function(n) info_node(n))

plot(airct)

```
