---
title: "Maladies cryptogamiques"
subtitle: "Pathogénèse et réponses de l'hôte"
author: "Sébastien GUYADER `r Sys.Date()`)"
date: 
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["tweak.css", "xaringan-themer.css", "footer-header.css", "animate.css", default]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
      navigation:
        click: true
    seal: false
    self_contained: false
---

```{r setup, include=FALSE, message=FALSE}
options(htmltools.dir.version = FALSE)
library(xaringanthemer)
mono_light(base_color = "#23395b")
```

class: title-slide, animated, fadeIn

# Maladies cryptogamiques : pathogénèse et réponses de l'hôte
### Sébastien GUYADER
#### INRA - UR Astro - Petit-Bourg

---

layout: true
class: main-slide, animated, fadeIn
<div class="my-footer"><span>S. Guyader &nbsp; - &nbsp; Maladies cryptogamiques : pathogénèse et réponses de l'hôte</span></div> 

---

class: middle

.pull-left[
* text 1
* text 2
* text 1
* text 2

```{r echo=FALSE, message=FALSE}
library(htmltools) ; library(DiagrammeR)
m <- mermaid("graph LR;
   id1(Start)-- text -->id2(Stop);
   style id1 fill:#f9f, stroke:#333, stroke-width:4px;
   style id2 fill:#ccf, stroke:#f66, stroke-width:2px, stroke-dasharray: 5, 5;
 ", height=100)
#htmlwidgets::saveWidget(m, 'diagram.html', background="transparent")
widgetframe::frameWidget(m)
```
]

.pull-right[
```{r echo=FALSE, message=F}
plot(cars)
```
]
---

layout: false
class: section-slide, inverse, center, middle, animated, fadeIn
<div class="my-footer"><span style="color:white">S. Guyader &nbsp; - &nbsp; Maladies cryptogamiques : pathogénèse et réponses de l'hôte</span></div>

# Nouvelle section

---

layout: true
class: main-slide, animated, fadeIn
<div class="my-footer"><span>S. Guyader &nbsp; - &nbsp; Maladies cryptogamiques : pathogénèse et réponses de l'hôte</span></div>

---

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

---

.left-column[
# Left column title
]
.right-column[
A whole sentence
  + one `Markdown` bullet point
{{content}}
]

--

  + a second bullet point
{{content}}

--

  + a third bullet point
{{content}}

--

    + a sub level
{{content}}

--
    + a second sub level
{{content}}

--

    + a third sub

---

#Last slide

> To see how it works <br/>
> quote and `inline code`

.blue-block[
exemple de bloc 
]

--
<br/>
.green-block[
exemple de bloc 
]

--
<br/>
.red-block[
exemple de bloc 
]

.footnote[.red.bold[*] Important footnote]