---
title: "Maladies cryptogamiques"
subtitle: "Pathogénèse et réponses de l'hôte"
author: "Sébastien GUYADER `r Sys.Date()`)"
date: 
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["tweak.css", "xaringan-themer.css", "footer-header.css", "animate.css", default]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
      click: true
    seal: false
    self_contained: false
---

```{r setup, include=FALSE, message=FALSE}
options(htmltools.dir.version = FALSE)
```
```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
mono_light(base_color = "#23395b")
```

class: title-slide, animated, fadeIn

# Maladies cryptogamiques : Pathogénèse et réponses de l'hôte
### Sébastien GUYADER
#### INRA - UR Astro - Petit-Bourg

---
layout: true
class: main-slide, animated, fadeIn
<div class="my-footer"><span>S. Guyader &nbsp; - &nbsp; Maladies cryptogamiques : Pathogénèse et réponses de l'hôte</span></div> 

---
class: middle

.pull-left[
* text 1
* text 2
* text 1
* text 2
<br/>
```{r echo=FALSE, message=FALSE, out.width="100%"}
library(htmltools) ; library(DiagrammeR)
DiagrammeR("
  graph LR;
  id1(Start)-- text -->id2(Stop);
  style id1 fill:#f9f,stroke:#333,stroke-width:4px;
  style id2 fill:#ccf,stroke:#f66,stroke-width:2px,stroke-dasharray: 5, 5;
")
```
]
.pull-right[
```{r echo=FALSE, message=F}
plot(cars)
```
]

---

class: center, middle

# xaringan

---
layout: false
class: section-slide, inverse, center, middle, animated, fadeIn
<div class="my-footer"><span>S. Guyader &nbsp; - &nbsp; Maladies cryptogamiques : Pathogénèse et réponses de l'hôte</span></div> 

# Get Started

---
layout: true
class: main-slide, animated, fadeIn
<div class="my-footer"><span>S. Guyader &nbsp; - &nbsp; Maladies cryptogamiques : Pathogénèse et réponses de l'hôte</span></div> 

---

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

---

.pull-left[
# Left column title

]
.pull-right[
A whole sentence

  + one `Markdown` bullet point
{{content}}

]

--

  + a second bullet point
{{content}}

--

  + a third bullet point
{{content}}

--

    + a sub level
{{content}}

--
    + a second sub level
{{content}}

--
    + a third sub
---

#Last slide

> To see how it works <br/>
> quote and `inline code`

.blue-block[
exemple de bloc 
]

