---
title: 'Principal Component Analysis'
author: 'Dataset CG.host_modif'
output:
  html_document: default
---
This dataset contains 30 individuals and 21 variables.

- - -

```{r, echo = FALSE}
load('Workspace.RData')
library(FactoMineR)
library(factoextra)
library(tidyverse)
```

# Study of the outliers
The analysis of the graphs leads to detect an outlier that strongly influences the results. First we will describe this outlier and then we will suppress it from the analysis.
Looking at the graph, we can note that a particular individual strongly contributes to the construction of the plane. Its contribution to the construction of the plane equals **38.9%**.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
CG.host_modif <- read.csv("CG.host_modif.csv", row.names=1)
res.PCA <- PCA(CG.host_modif[,1:21],graph=F,ncp=5)

drawn <- integer(0)
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.PCA(res.PCA, choix = 'ind', invisible = c('var', 'quali'), select = drawn, title = '', cex = cex)
```

**Figure 1.1 - Individuals factor map (PCA) before correction.** 
*Highlighting of an outlier.* 

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
CG.host_modif_cleaned <- slice(CG.host_modif, -1)
row.names(CG.host_modif_cleaned) <- rownames(CG.host_modif)[2:nrow(CG.host_modif)]
res.PCA_cleaned <- PCA(CG.host_modif_cleaned[,1:21],graph=F,ncp=5)

drawn <- integer(0)
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.PCA(res.PCA_cleaned, choix = 'ind', invisible = c('var', 'quali'), select = drawn, title = '', cex = cex)
```

**Figure 1.2 - Individuals factor map (PCA) after correction.** 
*Highlighting of an outlier.* 

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <- c("Composed.leaflets", "Simple.leaflets", "Height.max..cm.", 
"ovate.shape", "toothed.border", "Petiole.max..mm.", "obtuse.apex"
)
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.PCA(res.PCA, choix = 'var', select = drawn, title = '', cex = cex)
```

**Figure 1.3 - Variables factor map (PCA) before correction**
*The labeled variables are those the best shown on the plane.*

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <- c("Composed.leaflets", "Simple.leaflets", "Height.max..cm.", 
"ovate.shape", "toothed.border", "Petiole.max..mm.", "obtuse.apex"
)
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.PCA(res.PCA_cleaned, choix = 'var', select = drawn, title = '', cex = cex)
```

**Figure 1.3 - Variables factor map (PCA) after correction**

- - -

**The individual 1** :

- takes very high values for the variable(s) :
*Petiole.max..mm.*, *Lenght.max..cm.*, *lobed.border* and *webbed* (variables are sorted from the strongest).

- takes very low values for the variable(s) :
This outlier is suppressed from the analysis and a second one is performed on the rest of the individuals.

- - -

# Inertia distribution
The inertia of the first dimensions shows if there are strong relationships between variables and suggests the number of dimensions that should be studied.

The first two dimensions of PCA express **32.08%** of the total dataset inertia ; that means that 32.08% of the individuals (or variables) cloud total variability is explained by the plane.
This is an intermediate percentage and the first plane represents a part of the data variability.
This value is greater than the reference value that equals **28.71%**, the variability explained by this plane is thus significant
(the reference value is the 0.95-quantile of the inertia percentages distribution obtained by simulating 3441 data tables of equivalent size on the basis of a normal distribution).

From these observations, it may be interesting to consider the next dimensions which also express a high percentage of the total inertia.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
par(mar = c(2.6, 4.1, 1.1, 2.1))
barplot(res.PCA_cleaned$eig[,2], names.arg = 1:nrow(res.PCA_cleaned$eig))
```

**Figure 2 - Decomposition of the total inertia on the components of the PCA**

An estimation of the right number of axis to interpret suggests to restrict the analysis to the description of the first 1 axis.
These axis present an amount of inertia greater than those obtained by the 0.95-quantile of random distributions (19.62% against 15.98%).
This observation suggests that only this axis is carrying a real information.
As a consequence, the description will stand to these axis.

- - -

# Description of the dimension 1

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <- c("Passiflora foetida", "Euphorbia sp", "Indigofera spicata", 
"Datura stramonium", "Mimosa pudica", "Euphorbia heterophylla", 
"Passiflora", "Canavalia", "Teramnus labialis", "Indigofera sp", 
"Ludwigia octovalvis", "Calopogonium mucunoides", "Crotalaria retusa", 
"Vigna unguiculata", "Stachytarfeta jamaicensis", "Erechtites hieracifolia", 
"Euphorbia hirta (cyathophora) ou Chamaesyce Hirta")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.PCA(res.PCA_cleaned, select = drawn, axes = 1:2, choix = 'ind', invisible = 'quali', title = '', cex = cex)
```

**Figure 3.1 - Individuals factor map (PCA)**
*The labeled individuals are those with the higher contribution to the plane construction.*

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <- c("Composed.leaflets", "Simple.leaflets", "Height.max..cm.", 
"ovate.shape", "toothed.border", "Petiole.max..mm.", "obtuse.apex"
)
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.PCA(res.PCA_cleaned, select = drawn, axes = 1:2, choix = 'var', title = '', cex = cex)
```

**Figure 3.2 - Variables factor map (PCA)**
*The labeled variables are those the best shown on the plane.*

* * *

The **dimension 1** opposes individuals such as *Passiflora foetida*, *Erechtites hieracifolia*, *Ludwigia octovalvis*, *Euphorbia sp*, *Euphorbia hirta (cyathophora) ou Chamaesyce Hirta* and *Stachytarfeta jamaicensis* (to the right of the graph, characterized by a strongly positive coordinate on the axis)
to individuals such as *Indigofera spicata*, *Canavalia*, *Teramnus labialis*, *Calopogonium mucunoides*, *Vigna unguiculata* and *Indigofera sp* (to the left of the graph, characterized by a strongly negative coordinate on the axis).

The group in which the individuals *Ludwigia octovalvis* and *Euphorbia sp* stand (characterized by a positive coordinate on the axis) is sharing :

- high values for the variables *Height.max..cm.* and *pinnate.nervation* (variables are sorted from the strongest).

The group in which the individuals *Passiflora foetida*, *Erechtites hieracifolia*, *Euphorbia hirta (cyathophora) ou Chamaesyce Hirta* and *Stachytarfeta jamaicensis* stand (characterized by a positive coordinate on the axis) is sharing :

- high values for the variables *Opposite.disposition*, *toothed.border* and *Simple.leaflets* (variables are sorted from the strongest).
- low values for the variables *petiolate*, *ovate.shape*, *Composed.leaflets* and *pinnate.nervation* (variables are sorted from the weakest).

The group in which the individuals *Indigofera spicata*, *Canavalia*, *Teramnus labialis*, *Calopogonium mucunoides*, *Vigna unguiculata* and *Indigofera sp* stand (characterized by a negative coordinate on the axis) is sharing :

- high values for the variables *Composed.leaflets*, *ovate.shape*, *Petiole.max..mm.* and *obtuse.apex* (variables are sorted from the strongest).
- low values for the variables *Simple.leaflets*, *accute.apex*, *toothed.border* and *Height.max..cm.* (variables are sorted from the weakest).


- - -

# Classification

```{r, echo = FALSE}
res.hcpc_cleaned = HCPC(res.PCA_cleaned, nb.clust = -1, graph = FALSE)
```

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
drawn <- c("Passiflora foetida", "Euphorbia sp", "Indigofera spicata", 
"Datura stramonium", "Mimosa pudica", "Euphorbia heterophylla", 
"Passiflora", "Canavalia", "Teramnus labialis", "Indigofera sp", 
"Ludwigia octovalvis", "Calopogonium mucunoides", "Crotalaria retusa", 
"Vigna unguiculata", "Stachytarfeta jamaicensis", "Erechtites hieracifolia", 
"Euphorbia hirta (cyathophora) ou Chamaesyce Hirta")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res.hcpc_cleaned, choice = 'map', draw.tree = FALSE, select = drawn, title = '')
```

**Figure 4 - Ascending Hierarchical Classification of the individuals.**
*The classification made on individuals reveals 4 clusters.*


The **cluster 1** is made of individuals such as *Calopogonium mucunoides*, *Canavalia*, *Indigofera sp*, *Indigofera spicata*, *Teramnus labialis* and *Vigna unguiculata*. This group is characterized by :

- high values for the variables *Composed.leaflets*, *Petiole.max..mm.*, *ovate.shape* and *obtuse.apex* (variables are sorted from the strongest).
- low values for the variables *Simple.leaflets*, *toothed.border* and *Height.max..cm.* (variables are sorted from the weakest).

The **cluster 2** is made of individuals such as *Crotalaria retusa*, *Datura stramonium*, *Erechtites hieracifolia*, *Euphorbia hirta (cyathophora) ou Chamaesyce Hirta*, *Euphorbia sp*, *Ludwigia octovalvis* and *Stachytarfeta jamaicensis*. This group is characterized by :

- high values for the variables *Simple.leaflets*, *Height.max..cm.* and *toothed.border* (variables are sorted from the strongest).
- low values for the variables *Composed.leaflets*, *Petiole.max..mm.* and *Hairy.area* (variables are sorted from the weakest).

The **cluster 3** is made of individuals such as *Passiflora* and *Passiflora foetida*. This group is characterized by :

- high values for the variables *webbed* and *palmatipartite.shape* (variables are sorted from the strongest).

The **cluster 4** is made of individuals such as *Euphorbia heterophylla* and *Mimosa pudica*. This group is characterized by :

- high values for the variables *linear.shape* and *rounded.shape* (variables are sorted from the strongest).

- - -

# Other stuff to check:
```{r}
data_CG_host2 <- read.csv("data_CG_host2.csv", row.names=1)

data_CG_host2_cleaned <- slice(data_CG_host2, -1)
row.names(data_CG_host2_cleaned) <- rownames(data_CG_host2)[2:nrow(data_CG_host2)]

res.PCA2_cleaned <- PCA(data_CG_host2_cleaned[,1:21],graph=F,ncp=5)

pcaplot <- res.PCA2_cleaned %>% fviz_pca_biplot(repel=T, axes=c(1,2), title="", col.var="Black",
                            col.ind=data_CG_host2_cleaned$Colleto, palette="RdBu")
pcaplot


pcaplot_cleaned <- res.PCA2_cleaned %>% fviz_pca_biplot(repel=T, axes=c(1,2), title="",
                            geom.ind=c("text"))

pcaplot_cleaned +
  geom_point(aes(x=res.PCA2_cleaned$ind$coord[,1], y=res.PCA2_cleaned$ind$coord[,2],
                 col=data_CG_host2_cleaned$Colleto, shape=data_CG_host2_cleaned$Colleto)) +
  theme_bw()



CG.host_modif_cleaned2 <- CG.host_modif_cleaned
# i=2
# while(i < 17){
#   i=i+1
#   CG.host_modif_cleaned2[,i] <- as.factor(CG.host_modif_cleaned2[,i])
# }



res.FAMD <- FAMD(CG.host_modif_cleaned2[,1:21], sup.var=CG.host_modif_cleaned2[,24])

fviz_screeplot(res.FAMD)

fviz_famd_ind(res.FAMD)

# res.FAMD.ind <- res.FAMD[["ind"]][["coord"]]
# res.FAMD.var <- res.FAMD[["var"]][["coord"]]

# ggplot() +
#   geom_point(data=data.frame(res.FAMD.ind), aes(x=Dim.1, y=Dim.2), pch=1)+
#   geom_point(data=data.frame(res.FAMD.var), aes(x=Dim.1, y=Dim.2), fill="black")+
#   xlim(c(-4.2,4.2)) + ylim(c(-4,4))+
#   theme_bw()

fviz_famd(res.FAMD) +
  theme_bw()


```


# Annexes
```{r, comment = ''}
dimdesc(res.PCA_cleaned, axes = 1:1)
```
**Figure 5 - List of variables characterizing the dimensions of the analysis.**



```{r, comment = ''}
res.hcpc_cleaned$desc.var
```
**Figure 6 - List of variables characterizing the clusters of the classification.**


